---
title: "EMA Adherence EDA"
author: "Kendra wyant"
date: "`r lubridate::today()`"
format: 
  html:
    toc: true 
    toc_depth: 4
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

## Setup
```{r}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 
library(lubridate)
library(skimr)
library(patchwork)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

theme_set(theme_classic())
options(dplyr.print_max=Inf)

path_shared <- format_path("risk2/data_processed/shared")
```

## Read in data


```{r}
#| code-fold: true

ema <- read_csv(here::here(path_shared, "survey_daily.csv"), 
                show_col_types = FALSE) |> 
  mutate(start_date = with_tz(start_date,tzone = "America/Chicago"))

study_dates <- read_csv(here::here(path_shared, "study_dates_ema.csv"), 
                show_col_types = FALSE)

contact_log <- read_csv(here::here(path_shared, "contact_log.csv"), 
                show_col_types = FALSE) |> 
  select(subid, study_start = onboarding, study_end = study_termination) |> 
  filter(subid %in% ema$subid) |> 
  mutate(study_start = as_date(study_start, format = "%m/%d/%Y"),
         study_end = as_date(study_end, format = "%m/%d/%Y")) |> 
  filter(!subid %in% study_dates$subid) |> 
  left_join(ema |> 
              filter(!subid %in% study_dates$subid) |> 
              group_by(subid) |> 
              arrange(desc(start_date)) |> 
              slice_head(n = 1) |> 
              ungroup() |> 
              select(subid, ema_end = start_date),
            by = "subid")

study_dates <- study_dates |> 
  bind_rows(contact_log)

monthly <- read_csv(here::here(path_shared, "survey_monthly.csv"), 
                show_col_types = FALSE) |> 
  suppressWarnings()

context <- read_csv(here::here(path_shared, "gps_context.csv"), 
                show_col_types = FALSE) 
```


## Create days on study tibble

End 28 days before study end date

Get all study days for each subid
```{r}
# function to map over
get_study_days <- function(the_subid, dates) {
  study_start <- dates |>
    filter(subid == the_subid) |>
    pull(study_start)
  study_end <- dates |>
    filter(subid == the_subid) |>
    mutate(ema_end = date(ema_end),
           study_end = pmin(study_end, ema_end, na.rm = TRUE)) |>
    pull(study_end)
  if(study_end - study_start > 28) {
    study_days <- tibble(subid = the_subid,
                       study_day = seq(study_start,
                                       study_end - days(28),
                                       by = "day"))
    return(study_days)
  }
}

sub_days <- study_dates$subid |>
  map_dfr(~get_study_days(.x, study_dates))
```

Count EMAs per day with maximum value 1
```{r}
ema <- ema |>
  mutate(date = date(start_date)) |>
  group_by(subid, date) |>
  count() |>
  mutate(n = if_else(n > 1, 1, n)) |>
  ungroup()
```


Calculate number of EMAs in next 28 days for each subid and study_day in sub_days
```{r}
ema_count <- sub_days |>
  left_join(ema |>
              rename(survey_day = date),
            by = "subid",
            relationship = "many-to-many") |>
  filter(is.na(survey_day) | (survey_day > study_day &
                                survey_day <= study_day + 28)) |>
  group_by(subid, study_day) |>
  summarise(n_surveys = sum(!is.na(survey_day)),
            .groups = "drop")
```


Add 28-day periods with 0 EMAs back in
```{r}
ema_count <- ema_count |>
  right_join(sub_days, by = c("subid", "study_day")) |>
  mutate(n_surveys = if_else(is.na(n_surveys),
                                   0,
                                   n_surveys)) |>
  arrange(subid, study_day)
```


Calculate adherence for 28 day windows
```{r}
ema_count <- ema_count |>
  mutate(n_prompts = 28,
         adherence = n_surveys/n_prompts)
```


Add day number indicator
```{r}
ema_count <- ema_count |>
  group_by(subid) |>
  mutate(day_num = row_number()) |>
  ungroup()
```



### Update study end dates

```{r}
#| code-fold: true

get_labels <- function(the_subid, dates) {
  
  study_start <- dates |>  
    filter(subid == the_subid) |>  
    pull(study_start)
  
  study_end <- dates |>  
    filter(subid == the_subid) |> 
    mutate(ema_end = date(ema_end),
           study_end = pmin(study_end, ema_end, na.rm = TRUE)) |> 
    pull(study_end)
  
  if (study_end == study_start) {
      study_days <- tibble(subid = the_subid, 
                         study_day = seq(study_start, study_end, 
                                         by = "day")) 
  } 
  
  if (study_end != study_start) {
      study_days <- tibble(subid = the_subid, 
                         study_day = seq(study_start, study_end - days(1), 
                                         by = "day"))
    }
  
  return(study_days)
}
```


- 405 participants completed at least one daily survey
- 99195 labels

```{r}
length(unique(ema$subid))

unique(ema$subid) |> 
  map_dfr(~get_labels(.x, study_dates)) |> 
  nrow()
```

- 330 completed a monthly survey and provided GPS context data
- 96334 labels

```{r}
starting_sample <- monthly |> 
  filter(subid %in% context$subid) 

length(unique(starting_sample$subid))

unique(starting_sample$subid) |> 
  map_dfr(~get_labels(.x, study_dates)) |> 
  nrow()
```


Add new study end column that will be updated
```{r}
study_dates <- study_dates |> 
  filter(subid %in% starting_sample$subid) |> 
  mutate(study_end_ad = study_end)
```

Set compliance threshold for discontinuing. 

1. Any time adherence over the next 28 days falls below .33 discontinuation will be considered.

2. If adherence is below .33 for the majority of remaining days on study (< .75) they will be dropped.

3. If adherence is below .33 for less than the majority of remaining days on study (>= .75) they will be retained.

4. Discontinuation is considered every time adherence falls below .33

```{r}
for (sub in unique(study_dates$subid)) {
  study_days <- pull(subset(ema_count, subid == sub), study_day)
  adherence <- pull(subset(ema_count, subid == sub), adherence)
  
  for (i in seq_along(adherence)) {
    
    if(adherence[i] < .33) {
      
      prop_g_33 <- mean(adherence[i:length(adherence)] > .33)
                      
      if(prop_g_33 < .75) {
        study_dates <- study_dates |> 
          mutate(study_end_ad = if_else(subid == sub, study_days[i], study_end_ad))
        break
      }
    }
  }
}
```


89 subids have updated study_end dates
```{r}
study_dates |> 
  filter(study_end != study_end_ad) |> 
  glimpse()
```

316 have at least 28 days on study
```{r}
study_dates <- study_dates  |> 
  mutate(ema_end = date(ema_end),
         study_end_ad = pmin(study_end_ad, ema_end, na.rm = TRUE)) |> 
  mutate(on_study = as.numeric(study_end_ad - study_start)) |> 
  filter(on_study >= 28) 

nrow(study_dates)
```

85862 labels
```{r}
unique(study_dates$subid) |> 
  map_dfr(~get_labels(.x, study_dates |> 
                        mutate(study_end = study_end_ad))) |> 
  nrow()
```



Save out as new file that can be used for filtering labels

```{r}
study_dates |> 
  mutate(ema_end = date(ema_end),
         study_end_ad = pmin(study_end_ad, ema_end, na.rm = TRUE)) |> 
  select(subid, study_start, study_end_ad) |> 
  write_csv(here::here(path_shared, "study_end_ad_ema.csv"))
```



## Remake plots with updated end dates
```{r}
#| code-fold: true


ema_heat <- ema |> 
  left_join(study_dates |> select(subid, study_start, ema_end, study_end_ad),
            by = "subid") |> 
  mutate(study_end_ad = if_else(is.na(study_end_ad), ema_end, study_end_ad)) |> 
  group_by(subid) |> 
  filter(date <= study_end_ad) |> 
  ungroup()


ema_heat_count <- ema_heat |> 
  select(subid) |> 
  distinct() |> 
  left_join(ema_heat |> 
  group_by(subid) |> 
  filter(date > study_start & date < study_start + days(7)) |> 
  count() |> 
  mutate(week = 1) |> 
  ungroup(), by = "subid") |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(7) & date < study_start + days(14)) |> 
  count() |> 
  mutate(week = 2) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(14) & date < study_start + days(21)) |> 
  count() |> 
  mutate(week = 3) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(21) & date < study_start + days(28)) |> 
  count() |> 
  mutate(week = 4) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(28) & date < study_start + days(35)) |> 
  count() |> 
  mutate(week = 5) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(35) & date < study_start + days(42)) |> 
  count() |> 
  mutate(week = 6) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(42) & date < study_start + days(49)) |> 
  count() |> 
  mutate(week = 7) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(49) & date < study_start + days(56)) |> 
  count() |> 
  mutate(week = 8) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(56) & date < study_start + days(63)) |> 
  count() |> 
  mutate(week = 9) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(63) & date < study_start + days(70)) |> 
  count() |> 
  mutate(week = 10) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(70) & date < study_start + days(77)) |> 
  count() |> 
  mutate(week = 11) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(77) & date < study_start + days(84)) |> 
  count() |> 
  mutate(week = 12) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(84) & date < study_start + days(91)) |> 
  count() |> 
  mutate(week = 13) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(91) & date < study_start + days(98)) |> 
  count() |> 
  mutate(week = 14) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(98) & date < study_start + days(105)) |> 
  count() |> 
  mutate(week = 15) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(105) & date < study_start + days(112)) |> 
  count() |> 
  mutate(week = 16) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(112) & date < study_start + days(119)) |> 
  count() |> 
  mutate(week = 17) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(119) & date < study_start + days(126)) |> 
  count() |> 
  mutate(week = 18) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(126) & date < study_start + days(133)) |> 
  count() |> 
  mutate(week = 19) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(133) & date < study_start + days(140)) |> 
  count() |> 
  mutate(week = 20) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(140) & date < study_start + days(147)) |> 
  count() |> 
  mutate(week = 21) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(147) & date < study_start + days(154)) |> 
  count() |> 
  mutate(week = 22) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(154) & date < study_start + days(161)) |> 
  count() |> 
  mutate(week = 23) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(161) & date < study_start + days(168)) |> 
  count() |> 
  mutate(week = 24) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(168) & date < study_start + days(175)) |> 
  count() |> 
  mutate(week = 25) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(175) & date < study_start + days(182)) |> 
  count() |> 
  mutate(week = 26) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(182) & date < study_start + days(189)) |> 
  count() |> 
  mutate(week = 27) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(189) & date < study_start + days(196)) |> 
  count() |> 
  mutate(week = 28) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(196) & date < study_start + days(203)) |> 
  count() |> 
  mutate(week = 29) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(203) & date < study_start + days(210)) |> 
  count() |> 
  mutate(week = 30) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(210) & date < study_start + days(217)) |> 
  count() |> 
  mutate(week = 31) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(217) & date < study_start + days(224)) |> 
  count() |> 
  mutate(week = 32) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(224) & date < study_start + days(231)) |> 
  count() |> 
  mutate(week = 33) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(231) & date < study_start + days(238)) |> 
  count() |> 
  mutate(week = 34) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(238) & date < study_start + days(245)) |> 
  count() |> 
  mutate(week = 35) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(245) & date < study_start + days(252)) |> 
  count() |> 
  mutate(week = 36) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(252) & date < study_start + days(259)) |> 
  count() |> 
  mutate(week = 37) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(259) & date < study_start + days(266)) |> 
  count() |> 
  mutate(week = 38) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(266) & date < study_start + days(273)) |> 
  count() |> 
  mutate(week = 39) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(273) & date < study_start + days(280)) |> 
  count() |> 
  mutate(week = 40) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(280) & date < study_start + days(287)) |> 
  count() |> 
  mutate(week = 41) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(287) & date < study_start + days(294)) |> 
  count() |> 
  mutate(week = 42) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(294) & date < study_start + days(301)) |> 
  count() |> 
  mutate(week = 43) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(301) & date < study_start + days(308)) |> 
  count() |> 
  mutate(week = 44) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(308) & date < study_start + days(315)) |> 
  count() |> 
  mutate(week = 45) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(315) & date < study_start + days(322)) |> 
  count() |> 
  mutate(week = 46) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(322) & date < study_start + days(329)) |> 
  count() |> 
  mutate(week = 47) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(329) & date < study_start + days(336)) |> 
  count() |> 
  mutate(week = 48) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(336) & date < study_start + days(343)) |> 
  count() |> 
  mutate(week = 49) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(343) & date < study_start + days(350)) |> 
  count() |> 
  mutate(week = 50) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(350) & date < study_start + days(357)) |> 
  count() |> 
  mutate(week = 51) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(357) & date < study_start + days(364)) |> 
  count() |> 
  mutate(week = 52) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(364) & date < study_start + days(371)) |> 
  count() |> 
  mutate(week = 53) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(371) & date < study_start + days(378)) |> 
  count() |> 
  mutate(week = 54) |>  
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(378) & date < study_start + days(385)) |> 
  count() |> 
  mutate(week = 55) |> 
  ungroup()) |>
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(385) & date < study_start + days(392)) |> 
  count() |> 
  mutate(week = 56) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(392) & date < study_start + days(399)) |> 
  count() |> 
  mutate(week = 57) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(399) & date < study_start + days(406)) |> 
  count() |> 
  mutate(week = 58) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(406) & date < study_start + days(413)) |> 
  count() |> 
  mutate(week = 59) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(413) & date < study_start + days(420)) |> 
  count() |> 
  mutate(week = 60) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(420) & date < study_start + days(427)) |> 
  count() |> 
  mutate(week = 61) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(427) & date < study_start + days(434)) |> 
  count() |> 
  mutate(week = 62) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(434) & date < study_start + days(441)) |> 
  count() |> 
  mutate(week = 63) |> 
  ungroup()) |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(441) & date < study_start + days(448)) |> 
  count() |> 
  mutate(week = 64) |> 
  ungroup())  |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(448) & date < study_start + days(455)) |> 
  count() |> 
  mutate(week = 65) |> 
  ungroup())  |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(455) & date < study_start + days(462)) |> 
  count() |> 
  mutate(week = 66) |> 
  ungroup())  |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(462) & date < study_start + days(469)) |> 
  count() |> 
  mutate(week = 67) |> 
  ungroup())  |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(469) & date < study_start + days(476)) |> 
  count() |> 
  mutate(week = 68) |> 
  ungroup())  |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(476) & date < study_start + days(483)) |> 
  count() |> 
  mutate(week = 69) |> 
  ungroup())  |> 
  bind_rows(ema_heat |> 
  group_by(subid) |> 
  filter(date >= study_start + days(483) & date < study_start + days(490)) |> 
  count() |> 
  mutate(week = 70) |> 
  ungroup())

ema_heat_count <- ema_heat_count |>
  mutate(week = if_else(is.na(week), 1, week))
```




```{r}
#| code-fold: true

get_study_days <- function(the_subid, dates) {
  study_start <- dates |>  
    filter(subid == the_subid) |>  
    pull(study_start)
  study_end <- dates |>  
    filter(subid == the_subid) |> 
    mutate(ema_end = date(ema_end),
           study_end = pmin(study_end_ad, ema_end, na.rm = TRUE)) |> 
    pull(study_end)
  if(study_end - study_start > 28) {
    study_days <- tibble(subid = the_subid, 
                       study_day = seq(study_start, 
                                       study_end - days(28), 
                                       by = "day")) 
    return(study_days)
  }
}

sub_days <- study_dates$subid |> 
  map_dfr(~get_study_days(.x, study_dates))


ema_count <- sub_days |> 
  left_join(ema |> 
              rename(survey_day = date), 
            by = "subid",
            relationship = "many-to-many") |> 
  filter(is.na(survey_day) | (survey_day > study_day & 
                                survey_day <= study_day + 28)) |> 
  group_by(subid, study_day) |> 
  summarise(n_surveys = sum(!is.na(survey_day)),
            .groups = "drop")

ema_count <- ema_count |> 
  right_join(sub_days, by = c("subid", "study_day")) |> 
  mutate(n_surveys = if_else(is.na(n_surveys), 
                                   0, 
                                   n_surveys)) |> 
  arrange(subid, study_day)


ema_count <- ema_count |> 
  mutate(n_prompts = 28,
         adherence = n_surveys/n_prompts)

ema_count <- ema_count |> 
  group_by(subid) |> 
  mutate(day_num = row_number()) |> 
  ungroup()
```




```{r}
#| fig-width: 10
#| code-fold: true

subids <- unique(ema_count$subid) # 334 subids with end date or last ema date 28 days after start date

# split into groups of 10 plotting
subid_groups <- split(subids, ceiling(seq_along(subids) / 10))

map(subid_groups, function(ids) {
  plot_1 <- ema_count |>
    filter(subid %in% ids) |>
    ggplot(aes(x = day_num, y = adherence,
               group = subid, color = factor(subid))) +
    geom_line() +
    scale_x_continuous(breaks = seq(0, 364, 28), limits = c(0, 372)) +
    scale_y_continuous(breaks = c(.25, .5, .75, 1.0), limits = c(0, 1)) +
    # scale_color_manual(values = c("#0000F5", "#3BDFF5",
    #                               "#43DE49", "#DE43C7",
    #                               "#F59F3B")) +
    labs(color = NULL) +
    geom_hline(aes(yintercept = .50), linetype = "dashed") +
    geom_hline(aes(yintercept = .33), linetype = "dotted") +
    theme_classic()
  
  plot_2 <- ema_heat_count |>
    filter(subid %in% ids) |> 
    mutate(subid = factor(subid, levels = rev(ids))) |> 
    ggplot(aes(x = week, y = subid, fill = n)) + 
    geom_tile() +
    scale_fill_viridis_c(option = "C",
                         name = NULL,
                         na.value = "white") +
    scale_x_continuous(
      breaks = c(1, 4, 8, 12, 16, 20, 24, 28, 32, 36, 40, 44, 48, 52, 56, 
                 60, 64),
      limits = c(-1, 65),
      expand = c(0, 0)
    ) +
    labs(x = "Week number", y = "subid") +
    theme_minimal() +
    theme(panel.grid = element_blank()) +
    geom_vline(xintercept = 4) +
    geom_vline(xintercept = 52) +
    theme(legend.position = "bottom")
    
  plot_1 + plot_2
})
```


