---
title: "disposition"
author: "Kendra wyant"
date: "`r lubridate::today()`"
format: 
  html:
    toc: true 
    toc_depth: 4
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

## Setup
```{r}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 
library(lubridate)
library(skimr)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

theme_set(theme_classic())
options(dplyr.print_max=Inf)

path_shared <- format_path("risk2/data_processed/shared")
```

## Read in data


### screened/consented 420 participants
```{r}
contact_log <- read_csv(here::here(path_shared, "contact_log.csv"),
                        show_col_types = FALSE) |> 
  # filter out no shows
  filter(!is.na(consent)) |> 
  glimpse()
```



### On study

Defined as at least 1 ema in first and in second week on study

```{r}
ema <- read_csv(here::here(path_shared, "survey_daily.csv"),
                        show_col_types = FALSE) 


length(unique(ema$subid))
```






**Missing data/noncompliance with study procedures**

If one or more of the following conditions is met, participants will be withdrawn from the study with no option of re-enrolling (unless they have been incarcerated or enrolled in inpatient treatment).

- < 20 complete daily updates in any four-week period; > 2 missing lapse questions among completed daily updates in the same period.

- Failing to complete a total of three monthly updates.

- Failing to provide location data consistently by disabling location sharing for more than 12 hours in a four-week period.

### Lost 86 before month 1
```{r}
contact_log <- contact_log |> 
  mutate(excluded = if_else(subid == 1243 | subid == 1245, "excluded", excluded))
  
contact_log |>  
  filter(excluded == "excluded") |> nrow()
```

```{r}
contact_log <- contact_log |> 
  mutate(days_on_study = as.numeric(mdy(study_termination) - mdy(onboarding)))
```

```{r}
ema <- read_csv(here::here(path_shared, "survey_daily.csv"),
                show_col_types = FALSE)


ema_count <- ema |> 
  group_by(subid) |> 
  count() |> 
  rename(ema_n = n)

contact_log <- contact_log |> 
  left_join(ema_count, by = "subid")
```

#### 13 never enrolled officially after onboarding

- 4 never installed app
- no notes on other 9


```{r}
contact_log |> 
  filter(disposition == "never enrolled") |> 
  view()
```

#### 28 were withdrawn or discontinued before 


```{r}
contact_log |>  
  filter(excluded == "excluded" & disposition != "never enrolled" & days_on_study <= 31) |> view()
```


#### 334 made it to month 1
